Deep Reinforcement Learning for Conservation Decisions

### 2022-01-29 manuscript/manuscript.Rmd
Changing one issue name

\begin{table}
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{p{5 cm} p{10 cm}}
\hline
Issue & Description   \\
\hline
   Generalization                   & Agents struggle to adapt to tasks not seen in training.   \\
   Reproducibility                  & It can be very challenging to replicate results due to a host of reasons like differences in computational hardware. \\
   Intransparency                   & RL users cannot interpret why agents select actions. \\
   Hyperparameter Instability       & Agent performance can vary significantly over slight alterations in hyperparameters, like initialization seed.   \\
   Reward Misspecification          & Agents commonly learn undesirable behavior that still maximizes the RL objective. \\
   Capital Intensive                & Landmark successes like AlphaGo and AlphaStar have required very large teams of researchers and large amounts of computational power.  \\
   Sample Inefficiency              & Current algorithms require large amounts of interaction with the environment to achieve reward maximization.  \\

>>>>

\begin{table}
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{p{5 cm} p{10 cm}}
\hline
Issue & Description   \\
\hline
   Generalization                   & Agents struggle to adapt to tasks not seen in training.   \\
   Reproducibility                  & It can be very challenging to replicate results due to a host of reasons like differences in computational hardware. \\
   Lack of Transparency             & RL users cannot interpret why agents select actions. \\
   Hyperparameter Instability       & Agent performance can vary significantly over slight alterations in hyperparameters, like initialization seed.   \\
   Reward Misspecification          & Agents commonly learn undesirable behavior that still maximizes the RL objective. \\
   High Capital Demands            & Landmark successes like AlphaGo and AlphaStar have required very large teams of researchers and large amounts of computational power.  \\
   Sample Inefficiency              & Current algorithms require large amounts of interaction with the environment to achieve reward maximization.  \\
